Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-10-13 article.tex
Update resources table

				& $2\,438\,242$ & 988 & $21\,884$ &  &  running (increase snes-max-funcs)\\

@@

				& $319\,488$ & 154 & $4\,024$ 				&  & running  \\
				& $2\,555\,904$ & $1\,751$ & $22\,814$ 			&  &  \\

@@

			\textbf{Ventricle} & $1\,620$ & 54 & 133 				& & running \\
			\emph{3-D, static,}& $12\,960$ & 576 & 553 			& & \\
			\emph{hyperelastic} & $103\,680$ & $8\,362$ & $3\,435$ 	& & \\
				& $829\,440$ & $150\,023$ & $11\,746$ 			& & \\

@@

				& $36\,864$ & 2& 497 		& & running \\
				& $147\,456$ & 10& $1\,461$ 	& & \\

@@

			\textbf{Membrane ii} & 9 & x & x 	& 1 & 78 \\
			\emph{2-D, static,} & 36 & x & x 	& 2 & 78 \\
			\emph{hyperelastic} & 144 & x & x 	& 5 & 80 \\
				& 576 & x & x 			& 26 & 91 \\
				& $2\,304$ & x & x 		& & running \\
				& $9\,216$ & x & x 		& & \\
				& $36\,864$ & x & x 		& & \\
				& $147\,456$ & & $x$ 	& & \\

@@

			\textbf{Membrane iii} & 9 & x & x 		& 3 & 78 \\
			\emph{2-D, static,} & 36 & x & x 		& 6 & 79 \\
			\emph{hyperelastoplastic}& 144 & x & x	& 27 & 82 \\
				& 576 & x & x			& & running \\
				& $2\,304$ & x & x 		& & \\
				& $9\,216$ & x & x 		& & \\
				& $36\,864$ & x & x 		& & \\
				& $147\,456$ & & $x$ 	& & \\

@@

			\textbf{Cantilever} & $270$ & 11 & 85 		& & all diverged \\
			\emph{3-D, dynamic,} & $2\,160$ & 71 & 181 	& & \\
			\emph{hyperelastic}& $17\,280$ & 854 & 752 	& & \\
				& $138\,240$ & $11\,800$ & $5\,790$ 	& & \\

@@

	\caption{Execution times and maximum memory usage for Jacobian-free Newton-Krylov (JFNK) and segregated methods. Resource requirements are shown for the following cases: manufactured solution (MMS), XX }

>>>>

				& $2\,438\,242$ & 988 & $21\,884$ &  &  running (increase snes-max-funcs and max-it)\\

@@

				& $319\,488$ & 154 & $4\,024$ 				& $2\,916$ & $3\,547$  \\
				& $2\,555\,904$ & $1\,751$ & $22\,814$ 			&  &  running (increase snes-max-funcs and max-it)\ \\

@@

			\textbf{Ventricle} & $1\,620$ & 54 & 133 				& $\dag$ & $\dag$  \\ % & crashed at 0.23 s &  \\
			\emph{3-D, static,}& $12\,960$ & 576 & 553 			& $\dag$  & $\dag$ \\ % & crashed at 0.25 s & \\
			\emph{hyperelastic} & $103\,680$ & $8\,362$ & $3\,435$ 	& $\dag$  & $\dag$ \\ % & crashed at 0.18 s & \\
				& $829\,440$ & $150\,023$ & $11\,746$ 			& $\dag$  & $\dag$ \\ % & crashed at 0.16 s & \\

@@

				& $36\,864$ & 2& 497 		& 350 & re-run store mem \\
				& $147\,456$ & 10& $1\,461$ 	& & re-run increase max-it \\

@@

			\textbf{Membrane ii} & 9 	& 1 & 81 		& 1 & 78 \\
			\emph{2-D, static,} & 36 	& 1& 81 		& 2 & 78 \\
			\emph{hyperelastic} & 144 & 3 & 84 		& 5 & 80 \\
				& 576 			& 9 & 97 		& 26 & 91 \\
				& $2\,304$ 		& 34 & 144 	& 166 & 132  \\
				& $9\,216$ 		& 161 & 256  	& $1\,374$ & 357 \\
				& $36\,864$ 		&  &  	& $15\,991$ & $1\,053$ \\
				& $147\,456$ 		& rnng & 	& $135\,851$ & $2\,341$ \\

@@

			\textbf{Membrane iii} & 9 & $\dag$ & $\dag$	& 3 & 78 \\
			\emph{2-D, static,} & 36 & $\dag$ & $\dag$	& 6 & 79 \\
			\emph{hyperelastoplastic}& 144 & $\dag$ & $\dag$	& 27 & 82 \\
				& 576 & $\dag$ & $\dag$				& 231 & 104 \\
				& $2\,304$ & $\dag$ & $\dag$ 			& $1\,379$ & 180 \\
				& $9\,216$ & $\dag$ & $\dag$ 			& $8\,321$ & 451 \\
				& $36\,864$ & $\dag$ & $\dag$ 		& $60\,698$ & $1\,396$ \\
				& $147\,456$ & $\dag$ & $\dag$ 		& $341\,212$ & $3\,466$ \\

@@

			\textbf{Cantilever} & $270$ & 11 & 85 		& $\dag$ & $\dag$ \\
			\emph{3-D, dynamic,} & $2\,160$ & 71 & 181 	& $\dag$ & $\dag$ \\
			\emph{hyperelastic}& $17\,280$ & 854 & 752 	& $\dag$ & $\dag$ \\
				& $138\,240$ & $11\,800$ & $5\,790$ 	& $\dag$ & $\dag$ \\

@@

	\caption{Execution times (rounded to the nearest second) and maximum memory usage for Jacobian-free Newton-Krylov (JFNK) and segregated methods. $\dag$ indicates the solver crashed. }
